---
# This file represents a page section.
headless: true

# Order that this section appears on the page.
weight: 25

title: Past Editions
subtitle:

design:
  columns: '2'
---

ACCESS has been run twice so far, in 2024 and 2025, and, due to the dedication of the students and mentors, it has been a *[huge success](https://www.linkedin.com/pulse/when-ai-technology-revolutionises-biologists-vh3tf/?trackingId=yfMjRzJLxsUhWQjjFfDxJg%3D%3D)*, and we learnt a lot from each other.
ACCESS has attracted between 70 and 100 application each year, but we could only select 20 participants; we are thrilled to run the course again this year and offer this learning opportunity to more students!

Here are the past editions' websites: [ACCESS-2024 website](https://darsa.info/ACCESS-2024/), [ACCESS-2025 website](https://darsa.info/ACCESS-2025/). 

Gallery 2024

```{r, echo=FALSE, message=FALSE}
library(slickR)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )

opts <- slickR::settings(
  dots = TRUE,
  autoplay = TRUE,
  initialSlide = 0,
  slidesToShow = 2, 
  slidesToScroll = 2, 
  focusOnSelect = TRUE, 
  adaptiveHeight = FALSE)

slickR::slickR(
    sprintf("img/access-2024/%02d.jpg", 1:9),
    # height = 300,
    width = '100%') + opts
```

Gallery 2025

```{r, echo=FALSE, message=FALSE}
library(slickR)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )

opts <- slickR::settings(
  dots = TRUE,
  autoplay = TRUE,
  initialSlide = 0,
  slidesToShow = 2, 
  slidesToScroll = 2, 
  focusOnSelect = TRUE, 
  adaptiveHeight = FALSE)

slickR::slickR(
    sprintf("img/access-2025/%02d.jpg", 1:9),
    # height = 300,
    width = '100%') + opts
```
